---
title: "Open Peer Review"
author: "Tiara Verweij"
date: "20-4-2021"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
```
```{r import, echo=FALSE}
Review <- read_excel ("peerreview.xlsx")
```
**Abstract:**

Sickle cell disease results from a homozygous missense mutation in the ß-globin gene that causes polymerization of hemoglobin S. Gene therapy for patients with this disorder is complicated by the complex cellular abnormalities and challenges in achieving effective, persistent inhibition of polymerization of hemoglobin S. We describe our first patient treated with lentiviral vector-mediated addition of an antisickling ß-globin gene into autologous hematopoietic stem cells. Adverse events were consistent with busulfan conditioning. Fifteen months after treatment, the level of therapeutic antisickling ß-globin remained high (approximately 50% of ß-like-globin chains) without recurrence of sickle crises and with correction of the biologic hallmarks of the disease.

```{r, echo=FALSE}
Review
```
Ref: https://pubmed.ncbi.nlm.nih.gov/28249145/

